Using the internal language of toposes in algebraic geometry

### 2016-03-14 slides-pssl99.tex
typo

  \begin{block}{Motto}A topos is a category sufficiently rich to support
  an \hil{internal language}.
  \end{block}

@@

\note{\begin{itemize}\justifying
  \item While technically correct, the formal definition is actually
  misleading in a sense: A topos has lots of other vital structure, which
  is crucial for a rounded understanding, but is not listed in the
  definition (which is trimmed for minimality).

@@

  \item Check out an
  \href{https://ncatlab.org/publications/published/Leinster2011}{article by
  Tom Leinster} for a leisurely introduction to topos theory.
\end{itemize}}

@@

\note{\begin{itemize}\justifying
  \item The translation of internal statements into external ones is
  facilitated by an easy mechanical procedure which one quickly grows
  accustomed to.
  \item The internal language of a sheaf topos of a $\mathrm{T}_1$-space is
  \emph{classical} (that is, verifies the principle of excluded middle) if and
  only if the space is discrete. That's a not particularly interesting special
  case.
  \item See Section~2.4 of
  \href{https://rawgit.com/iblech/internal-methods/master/notes.pdf}{these
  notes} for remarks on how to appreciate intuitionistic logic.
\end{itemize}}

@@

  This gives an internal description of
  Monique Hakim's spectrum functor~$\mathrm{RT} \to \mathrm{LRT}$.
\end{frame}

@@

\begin{frame}\frametitle{More on the internal language}\justifying
  More generally, for an object~$U$ of a topos~$\E$, we define the meaning of
  \[ U \models \varphi \qquad\text{($\varphi$ holds on~$U$)}. \]
  Writing~``$\E \models \varphi$'' is then an abbreviation for~``$1 \models
  \varphi$'', where~``$1$'' denotes the terminal object of~$\E$.

>>>>

  \begin{block}{Motto}A topos is a category which is sufficiently rich to support
  an \hil{internal language}.
  \end{block}

@@

\note{\justifying
  While technically correct, the formal definition is actually
  misleading in a sense: A topos has lots of other vital structure, which
  is crucial for a rounded understanding, but is not listed in the
  definition (which is trimmed for minimality).

@@

  Check out an
  \href{https://ncatlab.org/publications/published/Leinster2011}{article by
  Tom Leinster} for a leisurely introduction to topos theory.
  \par
}

@@

\note{\begin{itemize}\justifying
  \item The translation of internal statements into external ones is
  facilitated by an easy mechanical procedure which one quickly grows
  accustomed to. \hyperlink{kripke-joyal}{\beamergotobutton{See more details.}}
  \item The internal language of a sheaf topos of a $\mathrm{T}_1$-space is
  \emph{classical} (that is, verifies the principle of excluded middle) if and
  only if the space is discrete. That's a not particularly interesting special
  case.
  \item See Section~2.4 of
  \href{https://rawgit.com/iblech/internal-methods/master/notes.pdf}{these
  notes} for remarks on how to appreciate intuitionistic logic.
\end{itemize}}

@@

  This gives an internal description of
  Monique Hakim's spectrum functor from ringed toposes to locally ringed
  toposes.
\end{frame}

@@

\begin{frame}[label=kripke-joyal]\frametitle{More on the internal language}\justifying
  More generally, for an object~$U$ of a topos~$\E$, we define the meaning of
  \[ U \models \varphi \qquad\text{($\varphi$ holds on~$U$)}. \]
  Writing~``$\E \models \varphi$'' is then an abbreviation for~``$1 \models
  \varphi$'', where~``$1$'' denotes the terminal object of~$\E$.
